\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-25 paper.qmd
Changed the MSE equation

$$
\text{MSE} = \sum_{j = 1}^{n} \frac{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}{b}
$$ {#eq-equation9}

Here, $b$ signifies the total number of bins, $p$ denotes the number of dimensions in the high-dimensional data, and $n$ represents the number of observations.

@@

$$
\text{AIC} = 2bp + np * log(\text{MSE})
$$ {#eq-equation10}

>>>>

$$
\text{MSE} = \sum_{j = 1}^{n} \frac{\sqrt{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}}{n}
$$ {#eq-equation9}

Here, $b'$ signifies the total number of bins without empty bins, $p$ denotes the number of dimensions in the high-dimensional data, and $n$ represents the number of observations.

@@

$$
\text{AIC} = 2b'p + np * log(\text{MSE})
$$ {#eq-equation10}

### 2024-01-25 paper.tex
Changed the MSE equation

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners, frame hidden, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

\begin{equation}\protect\hypertarget{eq-equation9}{}{
\text{MSE} = \sum_{j = 1}^{n} \frac{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}{b}
}\label{eq-equation9}\end{equation}

Here, \(b\) signifies the total number of bins, \(p\) denotes the number
of dimensions in the high-dimensional data, and \(n\) represents the
number of observations.

@@

\begin{equation}\protect\hypertarget{eq-equation10}{}{
\text{AIC} = 2bp + np * log(\text{MSE})
}\label{eq-equation10}\end{equation}

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{equation}\protect\hypertarget{eq-equation9}{}{
\text{MSE} = \sum_{j = 1}^{n} \frac{\sqrt{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}}{n}
}\label{eq-equation9}\end{equation}

Here, \(b'\) signifies the total number of bins without empty bins,
\(p\) denotes the number of dimensions in the high-dimensional data, and
\(n\) represents the number of observations.

@@

\begin{equation}\protect\hypertarget{eq-equation10}{}{
\text{AIC} = 2b'p + np * log(\text{MSE})
}\label{eq-equation10}\end{equation}

@@

\citet{Chen2023}
